Consistency scores in text data

### 2020-07-08 outputs/documents/paper.Rmd
ngram writeup WIP

>>>>

Without exception, all human languages have some words that co-occur more frequently with others. Under this assumption, we can regard the production of English text as a set of conditional probabilities, written as Pr($w_{k}$ | $w^{k-1}_{1}$), where $w_{k}$ is the predicted word and $w^{k-1}_{1}$ is the history of the word occuring in a sequence (citation). In other word, the generation of prediction $w_{k}$ is based on the history $w^{k-1}_{1}$. [Add more to link to n-gram]

N-gram is a sequence of n words. Taking the first sentence from the Jane Eyre excerpt as an example:

> There was no possibility of...

"There" is an unigram, "There was" is a bigram, "There was no" is a trigram, and "There was no possibility of" is a 5-gram. On the other hand, the trigrams of the exerpt are "There was no", "was no possibility" and "no possibility of". The overlapping chaining of words reveals the statstical behaviour in human language. Moreover, N-gram then enables us to assign a probability to the occurrence of a sequence of words or the probability of a word occurring next in a sequence of words.

[Include N to do more statistics write up]

The application of n-gram is versatile. N-gram is widely applied in text prediction and spelling-correction

> There was no possibility of taking a walk that day

This is useful because...

N-gram is a sequence of words that has n words in it. The n-gram model is widely applied to 
Since n-gram 
N-gram is a model that is widely applied to 
N-gram is under the assumtion that the production of English text can be characterized by a set of conditional probabilities, Pr($w_{k}$ | $w^{k-1}_{1}$), where $w_{k}$ is the prediction and $w^{k-1}_{1}$ is the history (Citation).
